Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-27 paper-ieee-trans.tex

\bibitem{cordis:egee}
\emph{Enabling Grids for E--sciencE (EGEE)} project, European Community Research and
Development Information Service (CORDIS).
[Online]. Available: \url{http://cordis.europa.eu/project/rcn/80149\_en.html}.
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee2}
\emph{Enabling Grids for E--sciencE--II (EGEE--II)} project, European Community Research and
Development Information Service (CORDIS).
[Online]. Available: \url{http://cordis.europa.eu/project/rcn/99189\_en.html}.
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee3}
\emph{Enabling Grids for E--sciencE--III (EGEE--III)} project, European Community
Research and Development Information Service (CORDIS).
[Online]. Available: \url{http://cordis.europa.eu/project/rcn/87264\_en.html}.
[Accessed 4 Jun. 2018].

@@

\bibitem{ggus}
T. Antoni \emph{et al.},
``Global grid user support—building a worldwide distributed user support infrastructure,''
\emph{J. Phys.: Conf. Ser.},
vol. 119, no. 5, 052002, 2008.

@@

\bibitem{cordis:egi-engage}
\emph{Engaging the EGI Community towards an Open Science Commons (EGI--ENGAGE)}
project, European Community Research and Development Information Service (CORDIS).
[Online]. Available: \url{http://cordis.europa.eu/project/rcn/194937\_en.html}.
[Accessed 4 Jun. 2018].

>>>>

\bibitem{cordis:egee}
\emph{Enabling Grids for E--sciencE (EGEE)} project, European Community Research and
Development Information Service (CORDIS).
[Online] Available: \url{http://cordis.europa.eu/project/rcn/80149_en.html}
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee2}
\emph{Enabling Grids for E--sciencE--II (EGEE--II)} project, European Community Research and
Development Information Service (CORDIS).
[Online] Available: \url{http://cordis.europa.eu/project/rcn/99189_en.html}
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee3}
\emph{Enabling Grids for E--sciencE--III (EGEE--III)} project, European Community
Research and Development Information Service (CORDIS).
[Online] Available: \url{http://cordis.europa.eu/project/rcn/87264_en.html}
[Accessed 4 Jun. 2018].

@@

\bibitem{ggus}
T. Antoni, et al.,
Global grid user support--building a worldwide distributed user support infrastructure,
\emph{J. Phys.: Conf. Ser.},
vol. 119, no. 5, 052002, 2008.

@@

\bibitem{cordis:egi-engage}
\emph{Engaging the EGI Community towards an Open Science Commons (EGI--ENGAGE)}
project, European Community Research and Development Information Service (CORDIS).
[Online] Available: \url{http://cordis.europa.eu/project/rcn/194937_en.html}
[Accessed 4 Jun. 2018].
